\textsf{Are frontier models superhuman chemists?}

### 2024-03-12 src/tex/ms.tex
include statistics about human baseline

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\citet{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study.

@@

To understand the current capabilities of \glspl{llm} in the chemical sciences, we evaluated a wide range of models on the chembench corpus, including systems augmented with external tools.
An overview of the results of this evaluation is shown in \Cref{fig:all_questions_models_completely_correct_radar}.

% Bar chart

@@

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
hat is, while users were prompted to not use external tools other than a calculator and to not consult with other humans, we do not have any way to verify that the participants complied with those rules. 
Note that users were also allowed to skip questions.

>>>>

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\citet{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study. The results shown in the main text are based on this subset. 
Results for the full corpus can be found in the appendix.

@@

To understand the current capabilities of \glspl{llm} in the chemical sciences, we evaluated a wide range of leading models\cite{Huggingface} on the chembench corpus, including systems augmented with external tools.
An overview of the results of this evaluation is shown in \Cref{fig:human_vs_models_bar}. In this figure, we show the percentage of questions that the models answered completely correctly.
We use horizontal bars to indicate the performance of various models and highlight statistics of the human performance with vertical lines.
The figure shows that the leading \gls{llm}, GPT-4, outperforms the best human in our study in this overall metric.
Many other models also outperform the average human performance.
% Bar chart

@@

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
That is, while users were prompted to not use external tools other than a calculator and to not consult with other humans, we do not have any way to verify that the participants complied with those rules. 
Note that users were also allowed to skip questions.

\paragraph{Participants}
Users were open to report about their experience in chemistry. 
\variable{output/num_users_with_education_info.txt} did so. 
Out of those, \variable{output/num_human_phd.txt} reported to have been awarded a Ph.D.
\variable{output/num_human_postdoc.txt} are beyond a first postdoc, \variable{output/num_human_master.txt} have a master's degree, and \variable{output/num_human_bachelor.txt} have a bachelor's degree and for \variable{output/num_human_highschool.txt} the highest awarded degree is from high school.
